Supplementary material

### 2020-04-23 analysis/paper/supplementary.Rmd
Changes to Supplementary materials - Labels changed to Supplementary table or figure - Added list of tables and figure - Minor spelling issues solved

---
title: "Supplementary material"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE
  )
```

@@

knitr::kable(flakes_metp1lp, booktabs=TRUE, caption = "Lapa do Picarerio - U/Lower T - mean and standard deviation of flake measurements (in mm).") %>% 
  row_spec(0, bold = T, align = "c") %>% 
  kable_styling(position = "center", font_size = 9, latex_options = "hold_position")

>>>>

---
title: "Supplementary material"
header-includes:
  - \usepackage{caption}
  - \captionsetup[figure]{name=Supplementary Figure,labelfont=it,labelsep = period}
  - \captionsetup[table]{name=Supplementary Table,labelfont=it,labelsep = period}  
output: 
  pdf_document: 
    latex_engine: xelatex
    fig_caption: no

---

\listoftables

\listoffigures

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE
  )

@@

knitr::kable(flakes_metp1lp, booktabs=TRUE, caption = "Lapa do Picareiro - U/Lower T - mean and standard deviation of flake measurements (in mm).") %>% 
  row_spec(0, bold = T, align = "c") %>% 
  kable_styling(position = "center", font_size = 9, latex_options = "hold_position")
